---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rprecommit

<!-- badges: start -->
![](https://img.shields.io/badge/github%20version-0.1.0-orange.svg)
[![R-CMD-check](https://github.com/alexym1/Rprecommit/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/alexym1/Rprecommit/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/alexym1/Rprecommit/branch/master/graph/badge.svg)](https://app.codecov.io/gh/alexym1/Rprecommit?branch=master)
<!-- badges: end -->

> Running precommit in R


## Overview

`Rprecommit` is a package that allows you to run pre-commit checks in R. This package is inspired by the package [lorenzwalthert/precommit](https://github.com/lorenzwalthert/precommit/tree/9525a2e1bb5fd00c813e2bd299a41ddbf915eddb).`Rprecommit` is designed to run pre-commit without any python dependencies. The package is still under development and new features will be added in the future.


## Installation

The latest version can be installed from GitHub as follows: 

```{r eval = FALSE}
install.packages("devtools")
devtools::install_github("alexym1/Rprecommit")
```


## Code of conduct

Please note that this project is released with a [Contributor Code of Conduct](https://alexym1.github.io/Rprecommit/CONTRIBUTING.html). By participating in this project you agree to abide by its terms.
